DRAFT: Week 3: Degree and Centrality

### 2022-03-04 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.4.22

# Week 2: Scripts
## Smuggler's Index: Network Attributes 
```{r Network Size}

@@

@@

  gd_snEL <- geodist(
    snEL, 
    inf.replace=Inf, 
    count.paths=TRUE, 
    predecessors=FALSE,
    ignore.eval=TRUE, 
    na.omit=TRUE)

@@

@@

  reachability(
    snEL,
    geodist.precomp=NULL,
    return.as.edgelist=FALSE,
    na.omit=FALSE)

@@

```{r iGraph:Nodes: Path: Length, echo=TRUE}
library(igraph)
# Head
list(
  head(V(igEL)$name,10),
  tail(V(igEL)$name,10)
  )

@@

```{r statnet: Dyad Census , echo=TRUE}
library(statnet)
library(sna)

    sna::dyad.census(snEL)
  print("statnet thinks it's an undirected network, so there are no mutual ties because it's an undirected network and the 'names' and 'ingredients' in a recipie do not have a reciprocal relationship. If anything the 'flow of info' moves from 'Drink Name' to 'Drink Ingredient' to 'Ingredient type'. The Drink name determines the recipie ingredients, but we're unable to identify a drink by calling on individual ingredients in a recipie")

    network.dyadcount(snEL)

```{r statnet: grecip: dyadic reciprocity & Mutuality, echo=TRUE}
library(statnet)
library(sna)

  grecip(snEL, 
         measure = "correlation")

```{r statnet: Triad Census, echo=TRUE}
library(sna)
#     Classify all Triad in the network:

#Directed Network
#**triad.census(snEL, mode="digraph")*

#     total number of all four triad types returned by triad census
snEL_sumTCensus  <- sum(
  sna::triad.census(
    snEL,
    mode="graph"))

list(   sna::triad.classify(
     snEL,
     tri=c(1,2,3),
     mode==c("digraph")
   ))
  #Classify the triads (1,2,3) and (2,3,4)

   triad.classify(snEL,tri=c(1:5))
   gplot(snEL,c[1:5])

```{r iGraph: Triad Census, echo=TRUE}
library(igraph)
#Classify all Triad in the network
list(igraph::triad_census(igEL))

```{r iGraph: weighted/ network transitivity, echo=TRUE}

#     network transitivity:
summary(
  transitivity(igEL)
)

summary(
igEL_guTrans <- transitivity(igEL,
             type = c("globalundirected"),
             vids = NULL, #  all vertices are considered.
             weights = NULL,
             isolates = c("NaN", "zero"))
)

summary(
  transitivity(igEL,
             type = c(
               "average"),
             vids = NULL, #  all vertices are considered.
             weights = NULL,
             isolates = c("NaN", "zero"))
)

#   c("undirected", "global", "globalundirected", "localundirected", "local","average", "localaverage","localaverageundirected", "barrat", "weighted")

```{r statnet: weighted/ directed network transitivity, echo=TRUE}

#     Directed Networks transitivity:
  gtrans(snEL)

#   methods for weighted networks, rank and correlation, along with the relevant references.
#  sna::gtrans()

## Ego Network Transivity or Clustering
`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.

, "KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH", 
                "YULETIDAL WAVE",
                "RUMBUSTION PUNCH",
                "PUKA PUNCH"
```{r iGraph:Local transitivity, echo=TRUE}
#     get global clustering cofficient
  transitivity(igEL, type="global")

#     check ego network transitivity
transitivity(igEL,
             type="local", 
             vids=V(igEL)[c(
               "AKU AKU", "SINGAPORE SLING", "HONDO HATTIE'S JUNGLE PUNCH!")]
               )
```

>>>>

# Week 2: Scripts

## Smuggler's Index: Network Attributes 
```{r Network Size}

@@

```{r iGraph: Dyad: Graph Density / Edge Density, echo=TRUE}
library(igraph)

  graph.density(igEL)

summary(
  graph.density(igEL)
)

    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network

  edge_density(igEL)

summary(
   edge_density(igEL)
)

      # Generating a random graph for comparison
# erdos.renyi.game
      ## In an erdos.renyi.graph, each edge has the same probability of being created. We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.

igEL_Nod <- vcount(igEL)

igEL_Den <- graph.density(igEL)

 igEL_randoGraph <- erdos.renyi.game(
    n = igEL_Nod, 
    p.or.m = igEL_Den, 
    directed = T) 
      # where n is the number of nodes, 
      # p.or.m is the probability of drawing an edge, 
      #directed is whether the network is directed or not
 class(igEL_randoGraph)
 summary(igEL_randoGraph)

 print_all(igEL_randoGraph)

plot(igEL_randoGraph,
      vertex.size = 5, 
      vertex.label = NA, 
      edge.curved = .1, 
      vertex.color = "tomato", 
      edge.arrow.size = .1, 
      edge.width = .5, 
     edge.color = "grey60")

```{r statnet: Dyad Count / Dyad Census , echo=TRUE}
library(statnet)
library(sna)

 network.dyadcount(snEL)
 sna::dyad.census(snEL)

     print("statnet thinks it's a directed network, so there are no mutual ties because it's an undirected network and the 'names' and 'ingredients' in a recipie do not have a reciprocal relationship. If anything the 'flow of info' moves from 'Drink Name' to 'Drink Ingredient' to 'Ingredient type'. The Drink name determines the recipie ingredients, but we're unable to identify a drink by calling on individual ingredients in a recipie")

```{r statnet: GRecip / Mutuality, echo=TRUE}
library(statnet)
library(sna)

    grecip(snEL, 
         measure = "correlation") 
```

```{r iGraph: Triad Census, echo=TRUE}
library(igraph)
#Classify all Triad in the network

sum(
  triad_census(igEL)
)

list(
  triad_census(igEL)
)

```
plot(
  triad_census(igEL)
)

```{r statnet: Triad Census / Triad Classify, echo=TRUE}
library(sna)

#     total number of all four triad types returned by triad census
sum(
  sna::triad.census(
    snEL,
    mode="graph"))

sna::triad.classify(
     snEL,
     tri=c(1,2,3),
     mode==c("graph")
   )

Perportion of connected triads to complete triads

```{r iGraph: Transitivity Network, echo=TRUE}
library(igraph)

# Calculate the maximal (weakly or strongly) connected components of a graph
igraph::cluster.distribution()

#     network transitivity:
 transitivity(igEL)

 summary(  
  transitivity(
   igEL,
   type = c("undirected"),
   vids = NULL, #  all vertices are considered.
   weights = NULL,
   isolates = c("NaN", "zero"))
)

summary( 
 transitivity(igEL,
             type = c("globalundirected"),
             vids = NULL, #  all vertices are considered.
             weights = NULL,
             isolates = c("NaN", "zero"))
)

summary(
  transitivity(igEL,
             type = c("localundirected"),
             vids = NULL, #  all vertices are considered.
             weights = NULL,
              isolates = c("NaN", "zero"))
)
#   c("undirected", "global", "globalundirected", "localundirected", "local","average", "localaverage","localaverageundirected", "barrat", "weighted")

```
plot(
  transitivity(igEL,
             type = c("localundirected"),
             vids = NULL, #  all vertices are considered.
             weights = NULL,
              isolates = c("NaN", "zero"))
)
```{r statnet: Transitivity:, echo=FALSE}
library(statnet)
library(sna)

#   Networks transitivity:
print("Networks transitivity:")  
print("Note: where missing values prevent the assessment of whether a triple is transitive, that triple is omitted.")

print("use.adjacency=FALSE -> 0: completely intransitive ")        
  gtrans(snEL,
         mode="digraph", #"digraph" for triads 
         use.adjacency=FALSE)

print("use.adjacency=TRUE -> 1: completely transitive")
  gtrans(snEL, 
         mode="graph", # No triads
         use.adjacency=TRUE)

# Unaffected by mode=digrag/graph, diag(nal)=F/T

#   measure = 
  ## c("weak", "strong", "weakcensus", "strongcensus", "rank", "correlation"),

print("Weak Ties: fraction of potentially intransitive triads returned")
  ## Weak Ties
  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("weak"),
    use.adjacency=FALSE)

  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("weak"),
     use.adjacency=TRUE)

print("weak census: total number of transitive triads is computed")  
  ## "weakcensus"
  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("weakcensus"),
    use.adjacency=TRUE)

  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("weakcensus"),
    use.adjacency=FALSE)

print("strong ties")  
  ## Strong Ties
  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("strong"),
    use.adjacency=TRUE)

  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("strong"),
    use.adjacency=FALSE)

print("strongcensus: total number of all (in/transitive) triad sets considered")
  ## "strongcensus"
gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("strongcensus"),
    use.adjacency=FALSE)

  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("strongcensus"),
    use.adjacency=TRUE)

print("rank")  
  ##  "rank"
gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c( "rank"),
    use.adjacency=FALSE)

  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c( "rank"),
    use.adjacency=TRUE)

  ## "correlation"
print("correlation: the matrix correlation of the valued adjacency matrix A with its second power (i.e., A^2), omitting diagonal entries where inapplicable.")

  gtrans(
    snEL,
    g=NULL,
    mode="graph", 
    measure = c("correlation"),
    use.adjacency=TRUE)

## Ego Network Transivity or Local Clustering

`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.

```{r iGraph: Local / Ego Network Transitivity, echo=TRUE}
#     get global clustering cofficient
  transitivity(igEL,
               type="global")

#     check ego network transitivity
transitivity(igEL,
             type="undirected",
             vids=V(igEL)[c(
               "AKU AKU", 
               "SINGAPORE SLING",
               "HONDO HATTIE'S JUNGLE PUNCH!")])

```{r statnet: Local / Ego Network Transitivity}
library(statnet)
library(sna)
print("Ego Network Transitivity")

print("use.adjacency=TRUE -> 1: completely transitive")
gtrans(
    snEL,
    g=snEL%v%"AKU AKU",
    use.adjacency=T)

gtrans(
    snEL,
    g=snEL%v%"LIME JUICE",
    use.adjacency=T)

print("use.adjacency=FALSE -> 0: completely intransitive ")        
gtrans(
    snEL,
    g=snEL%v%"AKU AKU",
    use.adjacency=FALSE)

gtrans(
    snEL,
    g=snEL%v%"LIME JUICE",
    use.adjacency=FALSE)

#   measure = 
  ## c("weak", "strong", "weakcensus", "strongcensus", "rank", "correlation"),

print("strong ties")  
  ## Strong Ties
  gtrans(
    snEL,
      g=snEL%v%"AKU AKU",
    mode="digraph", 
    measure = c("strong"),
    use.adjacency=FALSE)

  gtrans(
    snEL,
    g=snEL[c(
      "AKU AKU,KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH",
      "YULETIDAL WAVE","RUMBUSTION PUNCH", "PUKA PUNCH")],
    mode="graph", 
    measure = c("strong"),
    use.adjacency=FALSE)

  gtrans(
    snEL,
    g=snEL%v%"LIME JUICE",
    mode="graph", 
    measure = c("strong"),
    use.adjacency=F)

 gtrans(
    snEL,
     g=snEL[c(
       "LIME JUICE","2:1 SIMPLE SYRUP","ALLSPICE BERRIES",
       "APPLE BRANDY"  ,"ABSINTHE BLANC","AQUAVIT","AMARO AVERNA")],
    mode="graph", 
    measure = c("strong"),
    use.adjacency=F)

print("strongcensus: total number of all (in/transitive) triad sets considered")

print("strongcensus")
    ## "strongcensus"
  gtrans(
    snEL,
      g=snEL%v%"AKU AKU",
    mode="graph", 
    measure = c("strongcensus"))

gtrans(
    snEL,
    g=snEL[c(
      "AKU AKU,KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH",
      "YULETIDAL WAVE","RUMBUSTION PUNCH", "PUKA PUNCH")],
    mode="graph", 
    measure = c("strongcensus"))

gtrans(
    snEL,
   g=snEL%v%"LIME JUICE",
    mode="graph", 
    measure = c("strongcensus"))

  gtrans(
    snEL,
     g=snEL[c("LIME JUICE","2:1 SIMPLE SYRUP","ALLSPICE BERRIES","APPLE BRANDY"  ,"ABSINTHE BLANC","AQUAVIT","AMARO AVERNA")],
    mode="graph", 
    measure = c("strongcensus"))

@@

#uses a BFS to find the number and lengths of geodesics between all nodes

 gd_snEL <- geodist(
    snEL, 
    inf.replace=.5, #geodesics do not exist, substitute value
    count.paths=TRUE, 
    predecessors=T, # return predecessor list
    ignore.eval=F, # ignore edge values
    na.omit=F) # remove NA values

summary(gd_snEL)
view(
  list(gd_snEL))

@@

```
gplot(gd_snEL)
gplot(snEL_gdist)

@@

summary(
  reachability(
    snEL,
    geodist.precomp=NULL,
    return.as.edgelist=FALSE,
    na.omit=FALSE)
)
```

@@

```{r iGraph:Nodes: Path: Length, echo=TRUE}

library(igraph)
# Head
list(
  head(V(igEL)$name,10),
  tail(V(igEL)$name,10)
  )

@@
